Designing for Multiple Use and At-Risk Users: Tor Configuration Launcher

### 2016-03-29 pets2017-paper/pets2017-paper.tex
quantitative intro

\section{Quantitative Analyses of the Interfaces (Study 2)}

\subsection{Motivation}

>>>>

\section{Quantitative Analyses of the Interfaces (Study 2)}
We performed quantitative research to quantify the existing problems
and the impact of our redesign by generating numerical data to transform
into usable statistics. Specifically, we collected all events, transitions, 
and state for Tor Browser 5.0.3 and the redesigned Tor Browser. Participant
logs of how they interacted with each of these interfaces are used to both
quantify the issues we encountered in our previous qualitative 
study and to examine the differences in success rate, time to completion,
and configuration choices between the two versions.
